\documentclass[english]{../tktltiki}
\usepackage[pdftex]{graphicx}
\usepackage{subfigure}
\usepackage{url}
\begin{document}
\onehalfspacing

\title{Location Awareness - Week 1}

\author{Péter Ivanics}
\date{\today}

\maketitle

\numberofpagesinformation{\numberofpages\ pages}

\mytableofcontents

\section{Introduction}
	 
	 
\section{Location-based Services} 
	In the following subchapters, four Location Based Services (hereinafter LBSs) are introduced briefly. The first three - Commuter, Sport Tracker and Tinder - are consumer applications. They show some similarities in their business model and targeted audience as they freely available for everyone on today's popular mobile platform (iOS, Android and Windows Phone). However, they differ in their functionality as Commuter supports the usage of public transportation, Sport Tracker encourages the community to do physical exercises, while the Tinder is a dating application. The reason for describing these applications is their popularity, different focus and application area. As an active user, I have hands-on experience in all of them. In my opinion these applications are great specimen for this assignment.
	
	The last example is a mobile workforce management platform called Reslink. The reason of choosing this platform is its wide applicability, rich data and different focus compared to the other examples. In comparison to the previous examples, Reslink is a business-to-business platform operating in multiple business verticals. As one of the developers of the Reslink platform I believe that it serves as a splendid example of a LBS in the business field of workforce management. 
	
	\subsubsection{Commuter}
		% What is this solution briefly? Who is the targeted audience? 
		% How this solution uses location awareness? 
		% How does this solution address the challenges? Lack of standards, Positioning, Power consumption, Privacy
	% Tinder
		% What is this solution briefly? Who is the targeted audience? 
		% How this solution uses location awareness? 
		% How does this solution address the challenges? Lack of standards, Positioning, Power consumption, Privacy
	
	% Sport tracker
		% What is this solution briefly? Who is the targeted audience? 
		% How this solution uses location awareness? 
		% How does this solution address the challenges? Lack of standards, Positioning, Power consumption, Privacy
	% Reslink
		% What is this solution briefly? Who is the targeted audience? 
		% How this solution uses location awareness? 
		% How does this solution address the challenges? Lack of standards, Positioning, Power consumption, Privacy
\section{Privacy}
	
\section{Energy-efficiency}

\pagebreak

\nocite{*}

\bibliographystyle{tktl}
\bibliography{bibliorgaphy}

\lastpage
\appendices
\pagestyle{empty}
\end{document}


